---
title: "Peakfeatures_graphs"
author: "Saaz Sakrikar"
date: "11/13/2021"
output: html_document
---

Creates dot plots comparing avg peak width and%age of the genome covered by peaks, for halophilic histones vs halophilic TFs vs bacterial TFs vs bacterial NAPs.
Restricted to those where I could make reliable peak lists using Mosaics.
Avg peak widths and area covered by peaks is obtained simply using Excel and stored in Table S3 (which is the input for this code).

```{r setup}
#load required packages
library(readxl)
library(ggplot2)
library(forcats)
library(gridExtra)

#load input files
Peakcharacteristics=read_excel("TableS3_peakcharacteristics_Jul152022.xlsx",sheet = "TableS3")

Peaklocations_pval=read_excel("TableS4_hypergeometric_Jul152022.xlsx")

#Providing %age of the genome that is intergenic.
Hbt_inter=13.3
Hvo_inter=15.9
Hmed_inter=15.7
Hca_inter=14.1
Ec_inter=14.2
Sc_inter=26.6


```

# Plotting for Figure 3, main manuscript
```{r plotting}
#set the colors
my.colors<- c(Lrp = "darkorange", Bacterial_TF = "blueviolet",Euk_TF = "tan4",FIS = "khaki3",Halophilic_TF = "palevioletred",HNS = "black",HpyA = "darkblue",HstA = "cornflowerblue",IHF = "forestgreen")

#Average width of peaks
fig3a <- ggplot(Peakcharacteristics,aes(x=fct_inorder(Domain),y=Avg_width)) + 
  geom_dotplot(alpha=0.8,binaxis="y",  stackdir="center",aes(fill=Specific_classification,color=Specific_classification)) + 
  stat_summary(fun=median,fun.min=median,fun.max=median,geom="crossbar",colour = "grey60", width=0.35, alpha = 0.5)+ 
  theme_bw() + 
  scale_fill_manual(values = my.colors) + 
  scale_color_manual(values= my.colors) + 
  ylim(c(0,2000)) + 
  ggtitle("A") + 
  xlab("Domain of life") + 
  ylab("Avg width (bp)") + 
  theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(size=10),axis.title=element_text(family="sans",size=14,face="bold"))

#Percentage of genome covered by binding peaks
fig3b <- ggplot(Peakcharacteristics,aes(x=fct_inorder(Domain),y=Percent_covered)) + geom_dotplot(alpha=0.7,binaxis="y",binwidth=1,stackdir="center",aes(fill=Specific_classification,color=Specific_classification)) + 
  stat_summary(fun=median,fun.min=median,fun.max=median,geom="crossbar",colour = "grey60", width=0.35, alpha = 0.5) + 
  theme_bw() + 
  ylim(c(0,25)) + 
  scale_fill_manual(values= my.colors) + 
  scale_color_manual(values= my.colors) + 
  ggtitle("B") + 
  xlab("Domain of life") + 
  ylab("Percentage of genome covered by peaks") + 
  theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(size=10),axis.title=element_text(family="sans",size=14,face="bold"))


#Ordered by value
fig3c <-
ggplot(Peaklocations_pval,aes(y=percentinter,x=reorder(TF,percentinter))) + 
  geom_bar(aes(fill=Hypergeom_p),stat="identity") + 
  geom_segment(x=0.5,xend=1.5,y=Hbt_inter,yend=Hbt_inter,colour="red",size=2,lty=6) + 
  geom_segment(x=1.5,xend=2.5,y=Hvo_inter,yend=Hvo_inter,colour="red",size=2,lty=6) +
geom_segment(x=2.5,xend=3.5,y=Ec_inter,yend=Ec_inter,colour="red",size=2,lty=6) + 
  geom_segment(x=3.5,xend=4.5,y=Ec_inter,yend=Ec_inter,colour="red",size=2,lty=6) + 
  geom_segment(x=4.5,xend=5.5,y=Hca_inter,yend=Hca_inter,colour="red",size=2,lty=6) + 
  geom_segment(x=5.5,xend=6.5,y=Hvo_inter,yend=Hvo_inter,colour="red",size=2,lty=6) +
  geom_segment(x=6.5,xend=7.5,y=Hca_inter,yend=Hca_inter,colour="red",size=2,lty=6) + 
  geom_segment(x=7.5,xend=8.5,y=Hmed_inter,yend=Hmed_inter,colour="red",size=2,lty=6) + 
geom_segment(x=8.5,xend=9.5,y=Ec_inter,yend=Ec_inter,colour="red",size=2,lty=6) +
geom_segment(x=9.5,xend=10.5,y=Hvo_inter,yend=Hvo_inter,colour="red",size=2,lty=6) +
geom_segment(x=10.5,xend=11.5,y=Ec_inter,yend=Ec_inter,colour="red",size=2,lty=6) +
geom_segment(x=11.5,xend=12.5,y=Ec_inter,yend=Ec_inter,colour="red",size=2,lty=6) +
geom_segment(x=12.5,xend=13.5,y=Sc_inter,yend=Sc_inter,colour="red",size=2,lty=6) +
geom_segment(x=13.5,xend=14.5,y=Sc_inter,yend=Sc_inter,colour="red",size=2,lty=6) + 
  theme_bw() + 
  ylim(c(0,100)) + 
  ggtitle("C") + 
  xlab("Transcription Factor") + 
  ylab("Percentage intergenic") + 
  theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(family="sans",size=12,face="bold", hjust = 1, angle = 45),axis.title=element_text(family="sans",size=14,face="bold"))

pdf("fig3-pkfeatures-compiled-Jul2022.pdf", height = 11, width = 8)
grid.arrange (fig3a, fig3b, fig3c, nrow = 3)
dev.off()


```








```{r session}
sessionInfo()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
