---
title: "Peakfeatures_graphs"
author: "Saaz Sakrikar"
date: "11/13/2021"
output: html_document
---

Creates dot plots comparing avg peak width and%age of the genome covered by peaks, for halophilic histones vs halophilic TFs vs bacterial TFs vs bacterial NAPs.
Restricted to those where I could make reliable peak lists using Mosaics.
Avg peak widths and area covered by peaks is obtained simply using Excel and stored in Table S3 (which is the input for this code).

```{r setup}
library(readxl)
library(ggplot2)

Peakcharacteristics=read_excel("TableS3_peakcharacteristics.xlsx",sheet = "TableS3")
```


```{r plotting}
#Average widfth of peaks
ggplot(Peakcharacteristics,aes(x=Type_of_protein,y=Avg_width)) + geom_dotplot(alpha=0.8,binaxis="y",stackdir="center",aes(fill=Protein,color=Protein)) + stat_summary(fun=median,fun.min=median,fun.max=median,geom="crossbar",width=0.5) + theme_bw() + scale_fill_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + scale_color_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + ylim(c(0,2000)) + ggtitle("Avg width of ChIP-Seq peaks") + xlab("Type of protein") + ylab("Avg width (bp)") + theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(size=10),axis.title=element_text(family="sans",size=14,face="bold"))

#Percentage of genome covered by binding peaks
ggplot(Peakcharacteristics,aes(x=Type_of_protein,y=Percent_covered)) + geom_dotplot(alpha=0.8,binaxis="y",binwidth=1,stackdir="center",aes(fill=Protein,color=Protein)) + stat_summary(fun=median,fun.min=median,fun.max=median,geom="crossbar",width=0.5) + theme_bw()+ylim(c(0,25)) + scale_fill_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + scale_color_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + ggtitle("Total area under ChIP-Seq peaks") + xlab("Type of protein") + ylab("Percentage of genome covered by peaks") + theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(size=10),axis.title=element_text(family="sans",size=14,face="bold"))
```
Export plots to PDF
```{r pdf_export}
#pdf("Peak_width.pdf",height=4,width=6)

#Average widfth of peaks
#ggplot(Peakcharacteristics,aes(x=Type_of_protein,y=Avg_width)) + geom_dotplot(alpha=0.8,binaxis="y",stackdir="center",aes(fill=Protein,color=Protein)) + stat_summary(fun=median,fun.min=median,fun.max=median,geom="crossbar",width=0.5) + theme_bw() + scale_fill_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + scale_color_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + ylim(c(0,2000)) + ggtitle("Avg width of ChIP-Seq peaks") + xlab("Type of protein") + ylab("Avg width (bp)") + theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(size=10),axis.title=element_text(family="sans",size=14,face="bold"))
#dev.off()

#pdf("Peak_coverage.pdf",height=4,width=6)
#Percentage of genome covered by binding peaks
#ggplot(Peakcharacteristics,aes(x=Type_of_protein,y=Percent_covered)) + geom_dotplot(alpha=0.8,binaxis="y",binwidth=1,stackdir="center",aes(fill=Protein,color=Protein)) + stat_summary(fun=median,fun.min=median,fun.max=median,geom="crossbar",width=0.5) + theme_bw()+ylim(c(0,25)) + scale_fill_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + scale_color_manual(values=c("khaki4","blueviolet","black","darkblue","cornflowerblue","forestgreen","palevioletred","palevioletred","palevioletred")) + ggtitle("Total area under ChIP-Seq peaks") + xlab("Type of protein") + ylab("%age of genome covered by peaks") + theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.text.x=element_text(size=10),axis.title=element_text(family="sans",size=14,face="bold"))

#dev.off()
```


```{r session}
sessionInfo()
```