---
title: "Periodicity_of_nucleosome_sequences_combined"
author: "Saaz_Sakrikar"
date: "7/29/2020"
output: html_document
---

Made for a list of nucleosome centre locations in the genome. Requires the table of positions, and the fna genome sequence from NCBI. Picks out top 25% of nucleosomes (based on signal/noise ratio), if score is provided. Maps these back to the genome, by picking out histonesize around each centre. Concatenates all these strings from each nucleosome, and converts this into a binary based on AA/TT/TA presence (1 if dinucleotide is present, 0 otherwise). Finally, find the periodicity of this sequence using autoregression spectra.

This code combines the 3 inputs: Yeast histone from Widom et al Table S2, Hvo protected sites from Ammar et al eLife 2012 Table "Archaeal_browser_track_2N.bed", Thermococcus kodakarensis histone from Maruyama et al Table S4

```{r setup, warning=FALSE,error=FALSE}
#Load required libraries and scripts
library(seqinr)
library(pracma)
library(readxl)

source("convertseqtobinary_AATTTA2.R")
source("convertnucleosomecentrestobinary.R")
source("convertnucleosomecentrestobinary2.R")
source("convertnucleosomecentrestobinary3.R")
```


```{r load_data}
#Data for this run

Yeast_histonelength=160
Yeast_Nucleosomelist="Widom2012_S2.xlsx"
Yeast_Genome="GCF_000146045.2_R64_genomic.fna"

Hvo_histonelength=60
Hvo_Nucleosomelist="Ammar_centres.xlsx"
Hvo_Genome="Hfxvol.fna"

Thermok_histonelength=60
Thermok_Nucleosomelist="MaruyamaS4combined.xlsx"
Thermok_Genome="Thermok.fna"

```

This is the script that takes the table and converts it into a binary indicating the presence of AA/TT/TA dinucleotides.
spec.ar is the autoregression spectra of these dinucleotides for all the nucleosomes put together.

```{r periodicity_calculation,fig.show="FALSE"}
Yeast_allnucleosomesbinary=convertnucleosomecentrestobinary(Yeast_Nucleosomelist,Yeast_Genome,Yeast_histonelength)
Yeast_ARofnucleosomes=spec.ar(Yeast_allnucleosomesbinary)

Hvo_allnucleosomesbinary=convertnucleosomecentrestobinary2(Hvo_Nucleosomelist,Hvo_Genome,Hvo_histonelength)
Hvo_ARofnucleosomes=spec.ar(Hvo_allnucleosomesbinary)

Thermok_allnucleosomesbinary=convertnucleosomecentrestobinary3(Thermok_Nucleosomelist,Thermok_Genome,Thermok_histonelength)
Thermok_ARofnucleosomes=spec.ar(Thermok_allnucleosomesbinary)
```

Plot the 3 lines together
```{r plotting}
#Self-normalization for better visualisation
Yeast_normAR=Yeast_ARofnucleosomes$spec[,1]/mean(Yeast_ARofnucleosomes$spec[,1])
Hvo_normAR=Hvo_ARofnucleosomes$spec[,1]/mean(Hvo_ARofnucleosomes$spec[,1])
Thermok_normAR=Thermok_ARofnucleosomes$spec[,1]/mean(Thermok_ARofnucleosomes$spec[,1])

plot(Yeast_normAR,type="l",lwd=2,col="forestgreen",ylim=c(0.5,1.8))
lines(Hvo_normAR,lwd=2)
lines(Thermok_normAR,lwd=2,col="red")

```

Locating the precise location of the ~10bp peaks seen in the AR spectrum.
```{r precise_location_of_peak}
Yeast_peaklocs=findpeaks(Yeast_ARofnucleosomes$spec[90:110,1])
Yeast_actualpeakloc=Yeast_peaklocs[,2]+89
Yeast_Periodicity=1/Yeast_ARofnucleosomes$freq[Yeast_actualpeakloc]
print("Yeast")
print(Yeast_Periodicity)

Thermok_peaklocs=findpeaks(Thermok_ARofnucleosomes$spec[90:110,1])
Thermok_actualpeakloc=Thermok_peaklocs[,2]+89
Thermok_Periodicity=1/Thermok_ARofnucleosomes$freq[Thermok_actualpeakloc]
print("Thermok")
print(Thermok_Periodicity)
```