---
title: "Hvo_hstA_growth_Dec2021_salt"
output:
  html_document:
    df_print: paged
---

Plot growth curves of blank-corrected growth data, analyse area under the curve using grofit, and plot the resultant analysis as a boxplot.
Input is growth data from 3 different bioscreen runs, each containing 3 biological replicates and 2-3 technical reps per biorep, of OD600 data of, hstA KO (Hv253), and parent WT (Hv28) in low salt (HvYPC-L (1.5M NaCl), and high salt (HvYPC-H (4M NaCl) rich media.
Colour scheme throughout: blue=Hv28=parent=WT; red=Hv253=hstA=KO. 
Since area under the curve is being compared, I took care to cut off the data early into stationary phase (timestop=50 hrs) in order to not bias the results with a slightly different final OD in stat phase.


```{r loading,message=FALSE,warning=FALSE}
library(ggplot2)
library(forcats)
library(ggsignif)
library(grofit)
library(openxlsx)
library(readxl)
library(reshape2)

Growthtable=read_excel("Selectedbscr_data.xlsx")

#Information regarding strain names and run identifiers, used to separate data as needed.
Strains=c("Hv28","Hv253")
Media=c("YPCL","YPCH")
Runs=c("J17","F9","M11")
timestop=60
```

Converting data into a form which can be plotted - melting, removing tiny values, adding strain information.
```{r growthcurveprocessing}

Growthtablemelted=melt(Growthtable,id.vars="Time")

l1=length(Growthtablemelted$Time)

#Removing negative and very small positive values to allow plotting on log scale.
for (i in (1:l1)) {
  if (Growthtablemelted$value[i]<0.01) {
    Growthtablemelted$value[i]=0.01
  }
}

#Making a column with strain identifiers
l2=length(Strains)
strainvector=vector(length=l1)
strainvector=as.character(strainvector)
for (i in (1:l2)) {
  relrows=grep(Strains[i],Growthtablemelted$variable)
  strainvector[relrows]=Strains[i]
}

#Making a column with media identifiers
l3=length(Media)
mediavector=vector(length=l1)
mediavector=as.character(mediavector)
for (i in (1:l3)) {
  relrows=grep(Media[i],Growthtablemelted$variable)
  mediavector[relrows]=Media[i]
}

#Merging the column with  existing melted matrix

Growthtablemelted=cbind(Growthtablemelted,strainvector,mediavector)
colnames(Growthtablemelted)=c("Time","variable","OD","Strain","Media")
```


Plotting raw growth data prepared above. Semi-log plot.

```{r Curveplotting,warning=FALSE,message=FALSE}
for (i in (1:l3)) {
  melted=Growthtablemelted
  melted=melted[melted$Media==Media[i],]
  plot=ggplot(melted,aes(x=Time,y=OD,colour=Strain)) +
    scale_colour_manual(values=c("red","cadetblue3")) +
    scale_fill_manual(values=c("red","cadetblue3")) +
    geom_smooth(se=TRUE,level=0.99,aes(col=Strain,fill=Strain)) +
    theme_bw()+geom_line(size=0.1,alpha=0.35,aes(group=variable)) +
    xlim(c(0,timestop))+scale_y_log10()+ggtitle(paste(Media[i],"OD vs time - semi-log plot",sep=" ")) +
    xlab("Time (h)") +
    ylab("OD600") +
    theme(axis.text=element_text(family="sans",size=12,face="bold"),axis.title=element_text(family="sans",size=14,face="bold"))
  print(plot)
}

```

Preparing data as input into Grofit.
```{r grofitsetup}
#Separate OD from time data, get matrix transpose.
ODonly=Growthtable[,-1]

rowstop=timestop*2
rowstop=rowstop+1

ODonly_tstop=ODonly[1:rowstop,]
ODonly=t(ODonly)
ODonly_tstop=t(ODonly_tstop)

l4=length(ODonly[,1])
l4_tstop=length(ODonly_tstop[,1])
l5=length(ODonly[1,])

#3 rows of metadat required - full replicate info, strain, and batch.
Grofitmetadata=as.data.frame(matrix(nrow=l4,ncol=3))
Grofitmetadata[,1]=rownames(ODonly)

#Adding strain info
for (i in (1:l2)) {
  relrows=grep(Strains[i],Grofitmetadata[,1])
  Grofitmetadata[relrows,2]=Strains[i]
}

#Adding media info
for (i in (1:l3)) {
  relrows=grep(Media[i],Grofitmetadata[,1])
  Grofitmetadata[relrows,3]=Media[i]
}


#Putting together the matrix with metadata and OD data.
Grofitdatainput=cbind(Grofitmetadata,ODonly)
Grofitdatainput_tstop=cbind(Grofitmetadata,ODonly_tstop)


#Separate time matrix
l4=length(ODonly[1,])
l4_tstop=length(ODonly_tstop[1,])
l5=length(ODonly[,1])
Grofittimeinput=as.data.frame(matrix(nrow=l5,ncol=l4))
Grofittimeinput_tstop=as.data.frame(matrix(nrow=l5,ncol=l4_tstop))

for (i in (1:l5)) {
  Grofittimeinput[i,]=Growthtable$Time
  Grofittimeinput_tstop[i,]=Growthtable$Time[1:rowstop]
}
```

Measure area under curve using grofit, logistic model. log.y.gc option is used, meaning it is area  under curve in log-scale y-axis.
```{r Grofit}
Logisticmodelrates_tstop=gcFit(Grofittimeinput_tstop,Grofitdatainput_tstop,grofit.control(interactive=FALSE,log.y.gc = TRUE,model.type="logistic",suppress.messages=TRUE))
```

Visualise AUC distribution for hstA v WT
```{r Boxplot}
Grofitoutput_tstop=Logisticmodelrates_tstop$gcTable

#pdf("AUC-salt.pdf", height= 4, width = 6)
plot_list = list()
for (i in (1:l3)) {
  output=Grofitoutput_tstop
  output=output[output$concentration==Media[i],]
  
  plot = ggplot(output,aes(x=fct_rev(AddId),y=integral.model)) +
    geom_jitter(width=0.2,aes(color=AddId)) +
    stat_summary(fun=median,geom="crossbar",alpha=0.3,width=0.5,aes(color=AddId)) +
    scale_color_manual(values=c("red","cadetblue3")) +
    geom_signif(data=output,comparisons = list(c("Hv253","Hv28")),test="t.test",map_signif_level=TRUE)+ggtitle(paste(Media[i],"Area under semi-log curve vs genotype",sep=" ")) + 
    theme_bw() +
    xlab("Strain") +
    ylab("AUC") +
    theme(axis.text=element_text(family="sans",size=16,face="bold"),axis.title=element_text(family="sans",size=20,face="bold"))
  plot_list[[i]] = plot
}

for (i in 1:2) {
  
  #file_name = paste("AUC_salt", i, ".pdf", sep="")
  #pdf(file_name, width = 6, height = 4)
  print(plot_list[[i]])
  #dev.off()
}

#dev.off()
```

```{r sessioninfo}
sessionInfo()
```
