---
title: "FT of random sequences for comparison (new)"
output:
  html_document:
    df_print: paged
---

Generate sequences of a particular length (~=avg peak width) randomly from the genome (using main chromosome only for convenience and because only 5 of 62 peaks are in plasmids). Combine all these sequences together, as was done for the real peaks, and do the power spectru of the combination. Repeat this 100 times to get a nice sample.
Check the periodicity peak of each of these instances, and compare it to the known periodicity of the actual HpyA peaks (10.3bp).

```{r setup_inputs}
library(seqinr)
library(pracma)

source("generaterndomsequences.R")
source("convertseqtobinary_AATTTA.R")

NCBIgenome="Hbtsal.fna"
numberofregions=59
lengthofregions=300
```

``` {r generate_spectra}
spec=matrix(data=NA,nrow=100,ncol=500)
spec_GC=matrix(data=NA,nrow=100,ncol=500)

for (i in (1:100)) {
  spectra=generaterndomsequences(NCBIgenome,numberofregions,lengthofregions)
  spec[i,]=spectra$spec[,1]
}
```

``` {r analysgeneratedspectra}

relevantpeak=matrix(data=NA,nrow=100,ncol=2)

for (j in (1:100)) {
  peak=findpeaks(spec[j,85:115])
  if (length(peak[,1])>1) {
    bestpeakloc=which.max(peak[,1])
    relevantpeak[j,1]=peak[bestpeakloc,1]
    relevantpeak[j,2]=peak[bestpeakloc,2]
  }
  if (length(peak[,1])==1){
    relevantpeak[j,1]=peak[,1]
    relevantpeak[j,2]=peak[,2]
   }
  if (is.null(peak)) {
    relevantpeak[j,1]=0
    relevantpeak[j,2]=10
  }
}

relevantpeak[,2]=relevantpeak[,2]+84
relevantpeak[,2]=1000/relevantpeak[,2]
```

Make a plot with the location and height of each peak. Add the HpyA-bound regions as a separate point in red.

``` {r plot_results}

plot(relevantpeak[,2],relevantpeak[,1],pch=20,cex=0.75)
points(1000/97,0.081,type="p",col="red",pch=24,cex=1.5)
```
